---
title: "STged: Gene expression deconvolution in simulation study"
output:
  html_document: default
  pdf_document: default
  fontsize: 10pt
author: Jia-Juan Tu
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

#  Set the size of the figures
```{r, fig.height=7, fig.width=6, size="small", fig.align="center"}

```

# Set environment of Python modual
```{r}
#Please check the environment on you PC

python_env <- 'D:/Users/tujia/anaconda3/envs/ccnet/python.exe'
reticulate::use_python(python = python_env, required = TRUE)


anndata <- reticulate::import("anndata")
np <- reticulate::import("numpy")
sq <- reticulate::import("squidpy")

```

## Load function
```{r}

# Installation package

#  devtools::install_github("TJJjiajuan/STged")


library(STged)

# load data sets
data(Fishplus)

dim(sc_exp)
unique(sc_label)
dim(spot_exp)

head(spot_loc)

```



# Run STged step by step
**Note**: There are three steps in STged. We here give a small example to show how to run the code step by step.

## Step 1: clear data
```{r}

clean.only = FALSE
depthscale  = 1e6
datax = data_process(sc_exp = sc_exp,   sc_label = sc_label, 
                     spot_exp = spot_exp,  spot_loc = spot_loc,
                     depthscale = depthscale,  gene_det_in_min_cells_per = 0.01, 
                     expression_threshold = 0,
                     nUMI =  100, verbose = FALSE, clean.only = clean.only)

## Winsorize expression values to prevent outliers  
truncate = FALSE
if(truncate){
  qt = 0.05
  datax$sc_exp  =  winsorize(x =  datax$sc_exp, qt = qt)
  datax$spot_exp  =  winsorize(x =  datax$spot_exp, qt = qt)
}

```

## Step 2: construct spatial correlation structures
```{r}

cat("Construct spatial correlation", "\n")
L.mat = dis_weight(spot_loc = datax$spot_loc, spot_exp = datax$spot_exp, k = 6, 
                   quantile_prob_bandwidth = 1/3, method = "Hex", 
                   coord_type = "grid")


```

## Step 3: construct reference gene matrix
```{r}

cat("Construct reference gene matrix", "\n")
ref_exp = create_group_exp(sc_exp = datax$sc_exp, sc_label = datax$sc_label)

#the corresponding cell type proportion
beta =  beta[colnames(datax$spot_exp),]

```


## Step 4: run the main model
```{r}
cat("Run the STged", "\n")

start_time <- Sys.time()
stged.est = MUR.STged(srt_exp = datax$spot_exp, ref_exp = ref_exp, beta.type = beta,  W = L.mat$dis_weight, lambda1 = NULL, lambda2 = NULL,  cutoff = 0.05, epsilon = 1e-5,  
                      maxiter = 100)
end_time <- Sys.time()

cat("Run time of STged", end_time - start_time," seconds.\n")


```


## Alternatively, we can run the STged in one step
```{r eval=FALSE, warning=FALSE, include=TRUE}

start_time <- Sys.time()
model.est = STged(sc_exp = sc_exp, sc_label = sc_label, 
                  spot_exp = spot_exp, spot_loc = spot_loc,  beta = beta,
                  python_env = python_env,depthscale = 1e6,
                  knei = 6,  methodL =  "Hex",coord_type = "grid", 
                  quantile_prob_bandwidth = 1/3,
                  lambda1 = NULL, lambda2 = NULL, cutoff = 0.05, 
                  maxiter = 500,  epsilon = 1e-5)

end_time <- Sys.time()

cat("Run time of STged", end_time - start_time," seconds.\n")


```


